---
title             : "Påvirker tyggis konsentrasjonen i klasserommet?"
shorttitle        : "TYGGIS OG KONSENTRASJON"

author: 
  - name          : "Henrik Sørlie"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Akershus festning, Oslo"
    email         : "henrik.sorlie@uib.no"
  - name          : "Forfatter2"
    affiliation   : "1"
  - name          : "Forfatter3"
    affiliation   : "1"
  - name          : "Forfatter4"
    affiliation   : "1"
  - name          : "Forfatter5"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Forsvarets høgskole"
  - id            : "2"
    institution   : "Universitetet i Bergen"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "tyggis, konsentrasjon, klasserom, skole"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r data}
# I datasettet har klasse "1" fått tyggis. Klasse "2" har ikke fått tyggis.
data <- read.csv2("data/tyggisdata.csv")
```

<!-- Gruppe 1 jobber herfra... --->


<!-- ...til hit. -->
# Method
<!-- Gruppe 2 jobber herfra... --->
Dette er en eksperimentell studie hvor vi er på utkikk etter hvorvidt tyggis påvirker konsentrasjonen til elever på 5. trinn.
Elevene var delt i to klasser hvor begge klasser hadde likt undervisningsopplegg, men den ene klassen fikk utdelt tyggis, og den andre ikke. 
Klasse 1 fikk utdelt tyggis, klasse 2 er kontrollklasse uten tyggis. 

## Participants

Participants were `r printnum(length(data$ID))` student from two classes, with  
`r printnum(nrow(filter(data,Klasse==1)),numerals=FALSE,captilaze=FALSE)` students in class 1 and   `r printnum(nrow(filter(data,Klasse==2)),numerals=FALSE,captilaze=FALSE)` students in class 2. 

## Material

## Procedure


<!-- ...til hit. -->
## Data analysis
<!-- Gruppe 3 jobber herfra... --->

We used `r cite_r("r-references.bib")` for all our analyses.


# Results



<!-- ...til hit. -->
# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
