---
title             : "Påvirker tyggis konsentrasjonen i klasserommet?"
shorttitle        : "TYGGIS OG KONSENTRASJON"

author: 
  - name          : "Henrik Sorlie"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Akershus festning, Oslo"
    email         : "henrik.sorlie@uib.no"
  - name          : "Forfatter2"
    affiliation   : "1"
  - name          : "Forfatter3"
    affiliation   : "1"
  - name          : "Forfatter4"
    affiliation   : "1"
  - name          : "Forfatter5"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Forsvarets hogskole"
  - id            : "2"
    institution   : "Universitetet i Bergen"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "tyggis, konsentrasjon, klasserom, skole"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r data}
# I datasettet har klasse "1" fått tyggis. Klasse "2" har ikke fått tyggis.
data <- read.csv2("data/tyggisdata.csv")
```

<!-- Gruppe 1 jobber herfra... --->


<!-- ...til hit. -->
# Method
<!-- Gruppe 2 jobber herfra... --->

## Participants

## Material

## Procedure


<!-- ...til hit. -->
## Data analysis
<!-- Gruppe 3 jobber herfra... --->

We used `r cite_r("r-references.bib")` for all our analyses.


# Results

```{r}
data$sum.konsentrasjon <- data$spm1 + data$spm2 + data$spm3
data$sum.arbeidsro <- data$spm4 + data$spm5 + data$spm6
```

```{r}
library(MASS)
```

```{r}
tbl = table(data$Klasse, data$LÃ.ste.oppgaver) 
tbl                 # the contingency table

chisq.test(tbl) 
```

```{r}
data.klasse1 <- subset(data, Klasse =="1", select=c(LÃ.ste.oppgaver, sum.konsentrasjon, sum.arbeidsro))

data.klasse2 <- subset(data, Klasse =="2", select=c(LÃ.ste.oppgaver, sum.konsentrasjon, sum.arbeidsro))
```

Klasse 1 med tyggis hadde i snitt lost `r printnum(mean(data.klasse1$LÃ.ste.oppgaver))` oppgaver ($SD = `r printnum(sd(data.klasse1$LÃ.ste.oppgaver))`$). Klasse 2 uten tyggis hadde i snitt lost `r printnum(mean(data.klasse2$LÃ.ste.oppgaver))` oppgaver ($SD = `r printnum(sd(data.klasse2$LÃ.ste.oppgaver))`$).

Det var ikke signifinate forskjeller mellom klassene på antall utforte oppgaver.


```{r}
# independent 2-group t-test
t.test(data$sum.konsentrasjon~data$Klasse) # where y is numeric and x is a binary factor
```
```{r}
# independent 2-group t-test
t.test(data$sum.arbeidsro~data$Klasse) # where y is numeric and x is a binary factor
```

Klasse 1 med tyggis hadde i snitt en konsentrasjon på `r printnum(mean(data.klasse1$sum.konsentrasjon))`($SD = `r printnum(sd(data.klasse1$sum.konsentrasjon))`$). Klasse 2 uten tyggis hadde i snitt en konsentrasjon på `r printnum(mean(data.klasse2$sum.konsentrasjon))` ($SD = `r printnum(sd(data.klasse2$sum.konsentrasjon))`$).

```{r}
t1 <- t.test(data$sum.konsentrasjon~data$Klasse)
t2 <-t.test(data$sum.arbeidsro~data$Klasse)

library(broom)
library(purrr)

tab <- map_df(list(t1, t2), tidy)

tab[c("estimate", "statistic", "p.value", "conf.low", "conf.high")]
```





<!-- ...til hit. -->
# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
