---
title             : "Påvirker tyggis konsentrasjonen i klasserommet?"
shorttitle        : "TYGGIS OG KONSENTRASJON"

author: 
  - name          : "Henrik Sorlie"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Akershus festning, Oslo"
    email         : "henrik.sorlie@uib.no"
  - name          : "Forfatter2"
    affiliation   : "1"
  - name          : "Forfatter3"
    affiliation   : "1"
  - name          : "Forfatter4"
    affiliation   : "1"
  - name          : "Forfatter5"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Forsvarets hogskole"
  - id            : "2"
    institution   : "Universitetet i Bergen"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "tyggis, konsentrasjon, klasserom, skole"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(MBESS)
library(tidyverse)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r data}
# I datasettet har klasse "1" fått tyggis. Klasse "2" har ikke fått tyggis.
data <- read.csv2("data/tyggisdata.csv")
```

<!-- Gruppe 1 jobber herfra... --->


<!-- ...til hit. -->
# Method
<!-- Gruppe 2 jobber herfra... --->
This is an experimental study, where we are interested in wether chewing gum have an effect on the concentration to pupils in 5th grade.
The pupils are split in two classes, where one class were given chewing gum, and the other class were not.
Class 1 were given chewing gum, class 2 is the control group without chewing gum.

## Participants

Participants were `r printnum(length(data$ID))` student from two classes, with `r printnum(nrow(filter(data,Klasse==1)),numerals=FALSE,captilaze=FALSE)` students in class 1 and `r printnum(nrow(filter(data,Klasse==2)),numerals=FALSE,captilaze=FALSE)` students in class 2. 

## Material

Classwork working climate was measured with six Likert-type items wit agreement scale.
Sample items were: "I denne timen hadde jeg god arbeidsinnsats" og "I denne timen var det vanskelig å fokusere på det jeg skulle".
```{r}
digits<-3
omega.six <- ci.reliability(data = data[,c(5:10)], type="omega", conf.level = 0.95, interval.type="mlr", B = 10000)
```
Internal consistency was $\omega$ = `r printnum(omega.six$est, gt1 = FALSE, digits = digits)`, `r printnum(omega.six$conf.level*100, digits = 0)`% CI [`r printnum(omega.six$ci.lower, gt1 = FALSE, digits = digits)`, `r printnum(omega.six$ci.upper, gt1 = FALSE, digits = digits)`] .

## Procedure
Both classes were given the same lecture by the same teacher. 
Class 1 were given tyggis at the start of the class, and told that this was related to previous good behaviour.
All students were at the end of the class given a survey and asked to indicate how many tasks thay had finnished and answere six questions related to the class climate. 

<!-- ...til hit. -->
## Data analysis
<!-- Gruppe 3 jobber herfra... --->

We used `r cite_r("r-references.bib")` for all our analyses.


# Results



<!-- ...til hit. -->
# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
